{\fontfamily{ptm}\selectfont Reading Notes}

### 2025-05-31 Notebook LaTEX/Formalized Notes/Notes 2025 03/main.tex
>w<, changes

\chapter{Application, KKT of linear programming}

@@

    \section{Introductions and problem formulations}

@@

            \STATE{$z_1, p_0, \overline L_1, G^+:= \textbf{GMAPG}(f, g, x_{-1}, L, r_j, \rho, N_{\min}=n_0, N=M, \epsilon, \textbf{L}, \textbf{M}, \textbf{E}_{\chi}^a).$}

@@

                \IF{$M \le 0 \textbf{ or } G^+ \le \epsilon$}

@@

                \STATE{$z_{j + 1}, p_j, \overline L_{j + 1}, G^+ := \textbf{GMAPG}(f, g, z_j, \overline L_j, r, \rho, N_{\min}=n_j, N=M, \epsilon, \textbf{L}, \textbf{M}, \textbf{E}_{\chi}^a).$}

@@

@@

            Suppose that Algorithm \ref{alg:linear-rgmapg} is applied to it then the total number of iterations is bounded for all $M \in \N$, $\epsilon > 0$ by

@@

@@

        The final results from above theorem provides the convergence rate of iterates and the complexity of restart GMAPG under Assumption \ref{ass:q-growth-ch2}. 

@@

            Suppose $K = \sum_{i = 0}^{J - 1} p_i$ iteration were performed and, it achieved $G_0^{(J)} \le \epsilon$, 
            Now, let $k > 0$ and let $\epsilon = \sqrt{2}(F(z_0) - F^+)^{1/2}\exp(-k + 1)$ then: 

@@

                G_0^{(J)} &\le \epsilon = \sqrt{2}(F(z_0) - F^+)^{1/2}\exp(-k + 1)

@@

            Using Theorem \ref{thm:qfg-peb-equiv} from previous chapter and take note that Assumption \ref{ass:q-growth-ch2} is Definition \ref{def:necoara-weaker-scnvx}\ref{def:necoara-qfg}. 

@@

                G_0^{(J)} 

@@

                \item [(a)] 
                \item [(b)]
                \item [(c)]
                \item [(d)]

>>>>

\chapter{Application, Linear Feasibility Problems}

@@

    \section{Reducing LP to linear feasibility problems}
        We first introduce the linear feasibility problem as our primary problem. 

@@

            \STATE{$z_1, p_0, \overline L_1, G^{(0)}:= \textbf{GMAPG}(f, g, x_{-1}, L, r_j, \rho, N_{\min}=n_0, N=M, \epsilon, \textbf{L}, \textbf{M}, \textbf{E}_{\chi}^a).$}

@@

                \IF{$M \le 0 \textbf{ or } G^{(j-1)} \le \epsilon$}

@@

                \STATE{$z_{j + 1}, p_j, \overline L_{j + 1}, G^{(j)} := \textbf{GMAPG}(f, g, z_j, \overline L_j, r, \rho, N_{\min}=n_j, N=M, \epsilon, \textbf{L}, \textbf{M}, \textbf{E}_{\chi}^a).$}

@@

            Our goal now is to show that at iteration $j = s$ of Algorithm \ref{alg:linear-rgmapg} it must have $G_0 \le \epsilon$ at line 5 of Algorithm \ref{alg:gmapg}. 

@@

            Suppose that we applied Algorithm \ref{alg:linear-rgmapg} to it. 
            For any $\epsilon > 0$, assuming that it terminated at $j = J < M$ iteration.
            Then the total number of iterations has an upper bound:

@@

            This is one of the way the algorithm can terminate, making it a sufficient condition for deriving the upper bound on the total number of iterations. 

@@

        The final results from above theorem provide the convergence rate of iterates and the complexity of restart GMAPG under Assumption \ref{ass:q-growth-ch2}. 

@@

            Suppose a total of $K := \sum_{i = 0}^{J - 1} p_i$ iteration were performed and, at line 10 of Algorithm \ref{alg:linear-rgmapg} at iteration $j = J$ it achieved $G_0 \le \epsilon$ at line 5 of Algorithm \ref{alg:gmapg}. 
            That will cause the inner GMAPG to return $G_0$ so, at line 10 it has $G^{(J)} < \epsilon$ in Algorithm \ref{alg:linear-rgmapg}. 
            This is one of the ways the algorithm can terminate hence, it suffices for deriving an upper bound. 
            Now we show the convergence rate of $G^{(J)}$, let $k > 0$ and let $\epsilon = \sqrt{2}(F(z_0) - F^+)^{1/2}\exp(-k + 1)$ then: 

@@

                G^{(J)} &\le \epsilon = \sqrt{2}(F(z_0) - F^+)^{1/2}\exp(-k + 1)

@@

@@

                G^{(J)} 

@@

                \item [(a)] For the first equality, we assumed that $G^{(J)} < \epsilon$ in the outer loop and, it's returned by Algorithm \ref{alg:gmapg} at line 5. Therefore, it has $G_0 = G^{(J)} = \sqrt{L^{(J)}_0} \Vert z^{(J)} - x_0^{(J)}\Vert$ because it calls Algorithm \ref{alg:armijo-ls} (Armijo line search) with $\alpha_0 = 0$. The second equality comes by using Definition \ref{def:gm-for-ch2}. 
                \item [(b)] Proposition \ref{prop:bnded-lip-ls} has $L_0^{(J)} \le 2L$. 
                \item [(c)] Using Theorem \ref{thm:qfg-peb-equiv} from previous chapter and take note that Assumption \ref{ass:q-growth-ch2} is Definition \ref{def:necoara-weaker-scnvx}\ref{def:necoara-qfg}. 
                \item [(d)] The function $1/\sqrt{1 - x/L}$ is convex hence a Taylor expansion has $1/\sqrt{1 - x/L} \le 1 - x/(2L) $, substituting it with $x = \mu$ makes for a lower bound. 
